---
title: "bachelor_script_final"
output: html_document
date: "2023-05-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(tidyverse)
library(haven)
library(ggplot2)
library(lubridate)
library(readr)
library(dplyr)
library(knitr)
library(rvest)
library(tidyr)
library(kableExtra)
library(ggrepel)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/BACHELOROPPGAVEN")

environment <- readxl::read_xls("infringements_export_2023-04-05.xls")
```

## How many environmental infringement preocedings per country?

```{r}
count <- environment %>%
  group_by(Country) %>% 
  summarise(number_of_cases = n()) %>% 
  arrange(desc(number_of_cases))

head(count)
```

##Is there a correlation between high GDP and fewer environmental infringement cases?

Uploading GDP per capita data from the worldbank filtering for the most recent year: 2020 Obs: have to change Luxembourg to Luxemborg Then joining the two datasets to compare

```{r}

gdp <- read_csv("GDP_world_bank.csv", skip=3)
head(gdp)
gdp <- gdp %>%
  select(`Country Name`, `Country Code`, `2021`) %>% 
  rename("Country" = `Country Name`) %>% 
  rename("GDP" =`2021`)

gdp_inf <- gdp %>% 
  left_join(count,
    by= c("Country" = "Country")) %>% 
  drop_na()



ggplot(gdp_inf, aes(x =number_of_cases, y = GDP)) +
  geom_point(color = "darkred") +
  labs(title = "Does a higher GDP correlate to a lower number of\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "GDP (current US$)") +
  theme_bw() +
  geom_text_repel(aes(label = Country), size = 3)

```




## What about population size?

```{r}
population <- readxl::read_xlsx("population.xlsx", skip= 4)
head(population)

population <- population %>%
  select(`Country Name`,`2021`) %>% 
  rename("Country" = `Country Name`)


population <- population %>% 
  left_join(count,
    by= c("Country" = "Country")) %>% 
  drop_na()

ggplot(population, aes(x =number_of_cases, y = `2021`)) +
  geom_point(color = "darkgreen") +
  labs(title = "Does less populated countries have less environmental\ninfringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Population") +
  theme_bw() +
  geom_text_repel(aes(label = Country), size = 3)

```
# EU15

```{r}
#deleting rows
pop2 <- population[-c(3:5, 9, 13:15, 18:21, 23, 25,27),]

ggplot(pop2, aes(x =number_of_cases, y = `2021`)) +
  geom_point(color = "darkgreen") +
  labs(title = "EU15 Does less populated countries have less environmental\ninfringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Population") +
  theme_bw() +
  geom_text_repel(aes(label = Country), size = 3)
```


#Linear Regression analysis

```{r}
# making a new dataset with number of cases and GDP and population data


regression <- gdp_inf %>% 
  left_join(population,
    by= c("Country" = "Country"))


# Regression analysis
m1 <- lm(number_of_cases.x ~ GDP + `2021`, data = regression)
summary(m1)



tab_model(gdp_inf.lm)

tab_model(
  m1,
  pred.labels = c("intercept", "GDP", "population"),
  dv.labels = c("Environmental infringements"),
  string.pred = "Coeffcient",
  string.ci = "Conf. Int",
  string.p = "P-Value",
  digits.p= 4
)

```






## CAPACITY (MANAGEMENT)

#GDP per capita



```{r}
gdp2 <- read_csv("GDP_per_capita.csv", skip= 3)

gdp2 <- readxl::read_xlsx("GDP_per_capita.xlsx", skip= 4)

head(gdp2)
gdp2 <- gdp2 %>%
  select(`Country Name`,`2021`) %>% 
  rename("Country" = `Country Name`) %>% 
  rename(GDP_per_capita =`2021`)


options(scipen=0)

gdp_inf2 <- gdp2 %>% 
  left_join(count,
    by= c("Country" = "Country")) %>% 
  drop_na()


ggplot(gdp_inf2, aes(x =number_of_cases, y = GDP_per_capita)) +
  geom_point(color = "darkblue") +
  labs(title = "Does a higher GDP per capita correlate to a fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "GDP per capita (current US$)") +
  theme_bw() +
  geom_text_repel(aes(label = Country), size = 3)


```
# Only EU15

```{r}
#deleting rows
gdp_EU15 <- gdp_inf2[-c(3:5, 9, 14:15, 18:20, 22, 24,25),]


ggplot(gdp_EU15, aes(x =number_of_cases, y = GDP_per_capita)) +
  geom_point(color = "darkblue") +
  labs(title = "EU15: Does a higher GDP per capita correlate to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "GDP per capita (current US$)") +
  theme_bw() +
  geom_text_repel(aes(label = Country), size = 3)


```





```{r}
corruption <- readxl::read_xlsx("CPI2021_RegionalTables.xlsx", skip=2)

corruption.eu <- corruption %>% 
  filter(Region == "WE/EU") %>%
  select(c(`Country / Territory`, ISO3, Region, `CPI score 2021`, Rank)) %>% 
  rename("Country" = `Country / Territory`) %>% 
  rename("CPI_score_2021" =`CPI score 2021`)

corrupt_inf <- count %>% 
  left_join(corruption.eu,
            by= c("Country" = "Country"))


ggplot(corrupt_inf, aes(x = number_of_cases, y = CPI_score_2021)) +
  geom_point(color = "purple") +
  labs(title = "Do less corruption in the government lead to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Corruption index") +
  geom_text_repel(aes(label = Country), size = 3) +
  theme_bw()


```


# Only EU15

```{r}
#deleting rows
corrupt_new <- corrupt_inf[-c(7,12:18,20:21,24,26:28),]


ggplot(corrupt_new, aes(x = number_of_cases, y = CPI_score_2021)) +
  geom_point(color = "purple") +
  labs(title = "EU15: Do less corruption in the government lead to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Corruption index") +
  geom_text_repel(aes(label = Country), size = 3) +
  theme_bw()

```


# without EU15
```{r}
corrupt_rest <- corrupt_inf[-c(1:6,8:11, 19, 22:23, 25),]


ggplot(corrupt_rest, aes(x = number_of_cases, y = CPI_score_2021)) +
  geom_point(color = "purple") +
  labs(title = "Do less corruption in the government lead to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Corruption index") +
  geom_text_repel(aes(label = Country), size = 3) +
  theme_bw()

```


# Government efficiency 

```{r}
wb <- read_csv("30a2e06a-f048-4872-a472-1be336a435d6_Data.csv") %>% 
  drop_na()

wb_inf <-wb %>% 
  left_join(count,
            by= c("Country Name" = "Country"))

ggplot(wb_inf, aes(x = number_of_cases, y = `2021 [YR2021]`)) +
  geom_point(color = "darkgreen") +
  theme_bw() +
  labs(title = "Do a more efficient government lead to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Government efficiency index") +
  geom_text_repel(aes(label = `Country Name`), size = 3)


```

# EU 15

```{r}
wb_15 <- wb_inf[-c(3,4,8,9,14,16,17,20,22,24:27),]


ggplot(wb_15, aes(x = number_of_cases, y = `2021 [YR2021]`)) +
  geom_point(color = "darkgreen") +
  theme_bw() +
  labs(title = "EU15: Do a more efficient government lead to fewer\nenvironmental infringement proceedings?",
       x = "environmental infringement proceedings",
       y = "Government efficiency index") +
  geom_text_repel(aes(label = `Country Name`), size = 3)


```

# Regression analysis (capacity)

```{r}
corrupt.lm2 <- lm(number_of_cases ~ CPI_score_2021, data = corrupt_new)

summary(corrupt.lm2)




names(corrupt_inf)
corrupt.lm <- lm(number_of_cases ~ CPI_score_2021, data = corrupt_inf)

summary(corrupt.inf.lm)


tab_model(
  corrupt.lm2, corrupt.lm,
  pred.labels = c("Intercept", "Corruption index", "Corruption index EU15"),
  dv.labels = c("Number of environmental infringement proceedings", ""),
  string.pred = "Coeffcient",
  string.ci = "Conf. Int",
  string.p = "P-Value"
)
```



